---
title: "Visualization"
output: github_document
---

```{r}
library(tidyverse)
library(ggridges)

library(p8105.datasets)
data("weather_df")
```

Now we have everything we need!

```{r}
weather_df
```

Let's make a scatter plot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

I always like the dataframe first

```{r}
ggp_temp_scatterplpt = 
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()

ggp_temp_scatterplpt
```

Let's make this a bit fancier
The aestheetics are up to you

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(aes(color = name), alpha = 0.25) + 
  geom_smooth(se = FALSE)
```

Show faceting

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.5) +
  facet_grid(. ~ name)
```

Newer interface:
```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.5) +
  facet_grid(cols = vars(name))
```


Let's look at something else. 

```{r}
weather_df |> 
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp, alpha = 0.5)) + 
  geom_smooth(se = FALSE) +
  facet_grid((. ~ name))
```

make a plot of central park tmax vs tmin only, and covert temperatures to fahrenheit 

```{r}
weather_df |>
  filter(name == "CentralPark_NY") |>
  mutate(
    tmax = tmax * (9 / 5) + 32,
    tmin = tmin * (9 / 5) + 32
  ) |>
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```


what's a hex plot

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
```

## Univariate plots

```{r}
weather_df |>
  ggplot(aes(x = tmax, fill = name)) +
  geom_histogram() + 
  facet_grid(. ~ name)
```


Density plots are great!!

```{r}
weather_df |> 
  ggplot(aes(x = tmax, fill = name)) + 
  geom_density(alpha = 0.3)
```

Boxplots

```{r}
weather_df |> 
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot()
```

Violin plot

```{r}
weather_df |> 
  ggplot(aes(x = name, y = tmax)) +
  geom_violin()
```

Ridge plots -- helpful for the more variables you have compared to density plots

```{r}
weather_df |> 
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()
```

## Save some of my plots

```{r}
ggp_weather = 
weather_df |> 
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = 0.5) + 
  facet_grid(.~name)

ggp_weather

ggsave("ggp_weather.pdf", ggp_weather)
```

